Constraining the Interiors of Asteroids Through Close Encounters

### 2022-04-02 paper/main.tex
Updated paper

% The list of authors, and the short list which is used in the headers.
% If you need two or more lines of authors, add an extra line using \newauthor
\author[Jack T. Dinsmore]{
Jack T. Dinsmore,$^{1}$\thanks{E-mail: jtdinsmo@mit.edu}
Julien de Wit$^{2}$
\\
% List of institutions
$^{1}$Department of Physics, Massachusetts Institute of Technology\\
$^{2}$Department of Earth, Atmospheric, and Planetary Science, Massachusetts Institute of Technology
}

@@

@@

>>>>

% The list of authors, and the short list which is used in the headers.
% If you need two or more lines of authors, add an extra line using \newauthor
\author[Jack T. Dinsmore, Julien de Wit]{
Jack T. Dinsmore,$^{1}$\thanks{E-mail: jtdinsmo@mit.edu}
Julien de Wit$^{2}$
\\
% List of institutions
$^{1}$Department of Physics, Massachusetts Institute of Technology\\
$^{2}$Department of Earth, Atmospheric, and Planetary Science, Massachusetts Institute of Technology
}

@@

In section \ref{sec:scan-cadence}, we noted that posterior uncertainty as a function of observation cadence $\Delta t$ appears to increase suddenly near $\Delta t \sim 30-40$ min. We mentioned that this cadence cutoff is likely a function both of the period of the asteroid and the time spent near perigee. We study this cutoff in closer detal in this appendix.

@@

\ref{fig:cad-period} 
\ref{fig:cad-speed}

\begin{figure}
  \centering
  \includegraphics[height=0.89\textheight]{figs/cad-period.pdf}
  \caption{1-$\sigma$ confidence intervals plotted as a function of cadence $\Delta t$ for periods of 9 hr (the reference asteroid, solid colored lines), and 5 hours (dotted lines), and 20 hours (dashed lines). Confidence intervals have been normalized for the sake of comparison, so that the maximum for each curve is 1.}
  \label{fig:cad-period}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[height=0.89\textheight]{figs/cad-speed.pdf}
  \caption{1-$\sigma$ confidence intervals plotted as a function of the orbit time scaling $t/t_0$ for no scaling (the reference asteroid, solid colored lines), time doubling (dotted lines), and halving (dashed lines). See text for the definition of $t/t_0$. Confidence intervals have been normalized for the sake of comparison, so that the maximum for each curve is 1.}
  \label{fig:cad-speed}
\end{figure}
